Using reference models in variable selection \vspace{.1in}

### 2019-12-27 paper/ref_approach.tex
fixed few things from Juho comments + added iterative proj without a ref model in simulated experiment

An alternative to minimal subset variable selection is \emph{complete
  variable selection} in which the goal is to find all relevant
variables that have some predictive information about the target. In
complete variable selection, it is possible that there are theoretically
relevant variables, but given finite noisy data we are not able infer their relevance.
The projection predictive approach was originally designed for the minimal subset
variable selection but we will test a simple iterative variant for the complete
variable selection case in the section.
 In addition, we analyse the benefits of the reference
model approach in combination with three other
methods which have been specifically designed for complete variable selection. 
As the criteria of selection performance, we evaluate the average false
discovery rate and the average
sensitivity (i.e., the ratio of the number of relevant selected
variables over the total number of relevant variables). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \citet{paper:stability}.

@@

In our simulations, we use different levels of correlation 
$\rho\in\{0.3,0.5\}$ and numbers of
observations $n\in\{50,70,100\}$. The total number of variables $p$
and the number of relevant variables $k$ are fixed to $p = 1000$ and
$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
use a reference model which a Bayesian linear regression using the first five
supervised principal components (SPC) as variables and imposing an hierarchical prior on
their coefficients:
\begin{equation}
\label{eq:ref_mod}
\begin{aligned}
    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} \N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,\ldots,n \\
    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} \N(0,\tau^{2})\\
    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
    \end{aligned} &j=1,\ldots,5 \\ 
    &\sigma \sim t_{3}^{+}(0,10). \\
\end{aligned}
\end{equation}
In the above, $u_{ij}$ represents the $j$-th SPC evaluated at
observation $i$, and $s_{max}$ denotes the sample standard deviation
of the largest SPC.  The SPCs are computed using the
\texttt{R}-package \texttt{dimreduce} setting the screening threshold
parameter at $0.6s_{max}$.  In our experiments, the results are not
sensitive to the specific choice of the screening threshold, yet a more
principled approach would be to use cross-validation to select the
threshold as done by \citet{paper:projpred}.

>>>>

An alternative to minimal subset variable selection is \emph{complete
  variable selection} in which the goal is to find all relevant
variables that have some predictive information about the target. In
complete variable selection, it is possible that there are theoretically
relevant variables, but given finite noisy data we are not able infer their relevance.
The projection predictive approach was originally designed for the minimal subset
variable selection but we will test a simple iterative variant for the complete
variable selection case in the section.
 In addition, we analyse the benefits of the reference
model approach in combination with three other
methods which have been specifically designed for complete variable selection. 
As the criteria of selection performance, we evaluate the average false
discovery rate and the average
sensitivity (i.e., the ratio of the number of relevant selected
variables over the total number of relevant variables). We also provide
a comparison of the stability of the selection by means of a stability
measure proposed by \citet{paper:stability}, which goes from 0 to 1 and a higher value 
means a more stable selection.

@@

In our simulations, we use different levels of correlation 
$\rho\in\{0.3,0.5\}$ and numbers of
observations $n\in\{50,70,100\}$. The total number of variables $p$
and the number of relevant variables $k$ are fixed to $p = 1000$ and
$k = 100$, respectively. In general, the lower $\rho$ and $n$, the
more challenging the variable selection is. For this example, \citet{paper:projpred} proposed to
use a reference model which a Bayesian linear regression using the first five
supervised principal components (SPC) as variables and imposing an hierarchical prior on
their coefficients:
\begin{equation}
\label{eq:ref_mod}
\begin{aligned}
    Y_{i}|&\boldsymbol{\beta},\sigma^{2},\boldsymbol{u}_{i} \overset{ind}{\sim} \N(\boldsymbol{u}_{i}^{T}\boldsymbol{\beta},\sigma^{2}) \quad &i=1,\ldots,n \\
    &\beta_{j}|\!\begin{aligned}[t] &\tau \overset{iid}{\sim} \N(0,\tau^{2})\\
    &\tau \sim t_{4}^{+}(0,s_{max}^{-2}) 
    \end{aligned} &j=1,\ldots,5 \\ 
    &\sigma \sim t_{3}^{+}(0,10). \\
\end{aligned}
\end{equation}
In the above, $u_{ij}$ represents the $j$-th SPC evaluated at
observation $i$, and $s_{max}$ denotes the sample standard deviation
of the largest SPC.  The SPCs are computed using the
\texttt{R}-package \texttt{dimreduce} (\url{https://github.com/jpiironen/dimreduce}) setting the screening threshold
parameter at $0.6s_{max}$.  In our experiments, the results are not
sensitive to the specific choice of the screening threshold, yet a more
principled approach would be to use cross-validation to select the
threshold as done by \citet{paper:projpred}.
